State and Parameter Estimation for Spatio-Temporal Neural Fields

### 2010-06-16 ltx/Journal of Neuroengineering/StateAndParameterEstimationNeuralFields_JoNE.tex
merge changes

Given the basis function separation, the basis function width was set to $\sigma_{\phi}^2=2.5$~mm. This facilitated a smooth representation of the field by the basis function decomposition given the basis function separation and provided low-pass spatial filtering of the field. From equation~\ref{eq:WidthCutOffRelationship}, this allowed the basis function decomposition to represent spatial frequencies up to approximately $0.12$~Hz. The spatial frequency response of the basis functions can be seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
\begin{figure} 
	\begin{center}
		\subfigure[][]{\label{fig:ObservationFreqAnal}\includegraphics{./Graph/ObservationFrequencyResponse.pdf}}\\	
		\subfigure[][]{\label{fig:SensorFunctionFreqResponse}\includegraphics{./Graph/SensorChar.pdf}}
		\subfigure[][]{\label{fig:BasisFunctionFreqResponse}\includegraphics{./Graph/BasisChar.pdf}}
	\end{center}
	\caption{Spatial frequency analysis. \textbf{a.} Two-dimensional spatial frequency (in power dB, averaged over 400 time steps) of the observed field. The symmetry of the sensors and field basis functions allow for the 1-dimensional representation of the spectral characteristics. \textbf{b.} The spatial frequency response of a 1-dimensional model sensor. The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function. \textbf{c.} The spatial frequency response of a 1-dimensional neural field basis function. The dashed line shows the cut-off frequency (-3 dB point).} 
\end{figure}

\subsection{State and Parameter Estimates} 
\label{sec:state_and_param_results}
To demonstrate the performance of the parameter and state estimation, a Monte Carlo approach was employed where $100$ realisations of the data were generated. Each realisation consisted of $500$~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out. The initial state and parameters were unknown to the estimator. Six iterations of the estimation algorithm were required for the parameters to converge.

>>>>

Given the basis function separation, the basis function width was set to $\sigma_{\phi}^2=2.5$~mm. This facilitated a smooth representation of the field by the basis function decomposition given the basis function separation and provided low-pass spatial filtering of the field. From equation~\ref{eq:WidthCutOffRelationship}, this allowed the basis function decomposition to represent spatial frequencies up to approximately $0.12$~Hz. The spatial frequency response of the basis functions can be seen in Figure~\ref{fig:BasisFunctionFreqResponse}.
\begin{figure} 
	\begin{center}
		\subfigure[][]{\label{fig:ObservationFreqAnal}\includegraphics{./Graph/ObservationFrequencyResponse.pdf}}\\	
		\subfigure[][]{\label{fig:SensorFunctionFreqResponse}\includegraphics{./Graph/SensorChar.pdf}}
		\subfigure[][]{\label{fig:BasisFunctionFreqResponse}\includegraphics{./Graph/BasisChar.pdf}}
	\end{center}
	\caption{Spatial frequency analysis. \textbf{a.} Two-dimensional spatial frequency in power dB, averaged over 400 time steps) of the observed field. The symmetry of the sensors and field basis functions allow for the 1-dimensional representation of the spectral characteristics. \textbf{b.} The spatial frequency response of a 1-dimensional model sensor. The dashed line shows the cut-off frequency (-3 dB point), indicating a wider bandwidth than the field basis function. \textbf{c.} The spatial frequency response of a 1-dimensional neural field basis function. The dashed line shows the cut-off frequency (-3 dB point).} 
\end{figure}

\subsection{State and Parameter Estimates} 
\label{sec:state_and_param_results}
To demonstrate the performance of the parameter and state estimation, a Monte Carlo approach was employed where $100$ realisations of the data were generated. Each realisation consisted of $500$~ms of data (sampled at $1$~kHz) and the estimation was applied to the final $400$~ms, allowing the model's initial transients to die out. The initial state and parameters were unknown to the estimator. Six iterations of the estimation algorithm was sufficient to allow the parameters to converge.
